--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
#bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "The output format for this example is bookdown::gitbook."
---

# Stage Sucrivoire Zuénoula




## Les librairies

```{r message = FALSE, warning = FALSE}
library("ggpubr")    # ggboxplot()
library("agricolae") # SNK.test() Student Newman-Keuls
library("car")       # leveneTest()
library("Rmisc")     # summarySE()
library("rstatix")   # identify_outliers()
library("tidyverse") # tidy et ggplot2
```

How do we save our ANOVA test, in a situation where the homogeneity of variance assumption is violated ?

welch_anova_test() [rstatix] : peut être utilisé lorsque l’hypothèse d’homogénéité de variance est violée (alors que normalité est respectée ? - vérifier), comme dans notre exemple.

An alternative procedure (i.e.: Welch one-way test), that does not require that assumption have been implemented in the function `oneway.test()` or `welch_anova_test()`.

ANOVA test with no assumption of equal variances

```{r}
oneway.test(weight ~ group, data = my_data)
```

Pairwise t-tests with no assumption of equal variances

```{r}
pairwise.t.test(my_data$weight, my_data$group, p.adjust.method = "BH", pool.sd = FALSE)
```


```{r}
tab_mc <- (SNK.test(lm, "Engrais", group = TRUE))$groups %>% 
  mutate(Engrais = rownames(.)) %>% 
  select(Engrais, dPass, groups) %>% 
  as_tibble()
tab_mc
```


